Author disambiguation of large-scale semi-labeled collections of scientific articles

### 2015-08-18 paper.tex
implementation

\glnote{To proofread / improve}

Having the algorithm split into three elements, we implemented each of them separately.
Learning a similarity function and semi-supervised clustering steps required sophisticated
machine learning algorithms which implementations transcended the scope of this project.
Thus, we used ready-to-go \textit{Scikit-learn} library \citep{scikit-learn} and
semi-supervised clustering from \textit{SciPy} \citep{scipy}. In order to keep the code
maintainable and abstract, we followed practices introduces by \textit{Scikit-learn API}
\citep{scikit-learn-API}.

Performance-wise, the clustering step appeared to be the bottleneck. We improved the
algorithmic efficiency by parallelizing it. Having $n$ cores available, one can run the
semi-supervised clustering for $n$ different blocks in the same moment. In the production
systems the disambiguation often need not be run on the whole dataset. Once the dataset has
been disambiguated once, it is possible to avoid rerunning the whole algorithm when the new
signatures arrive in the digital library. First of all, the similarity function can be
reused. Moreover, the clustering has to be applied only to the blocks the new signatures are
contained within.

\msnote{Fill the table with times}
\msnote{Add times for clustering with phonetic blockings if they prove to be better}

\FloatBarrier
\begin{table}[H]
\caption{Time performance (2 GHz per CPU core, 32GB RAM)}
\centering
\begin{tabular}{|l|l|}
  \hline
  \textbf{algorithm} & \textbf{time}\\
  \hline
  blocking 1200000 signatures & dfsf \\
  \hline
  learning similarity function on 1000 pairs on reduced set of features & w1k2\\
  \hline
  learning similarity function on 1000000 pairs on reduced set of features & w2k2 \\
  \hline
  learning similarity function on 1000000 pairs on full set of features & sdfsdf \\
  \hline
  clustering 1200000 signatures on reduced set of features using 16 cores & asdsda \\
  \hline
  clustering 1200000 signatures on reduced set of features using 1 cores & aasdfs \\
  \hline
  clustering 1200000 signatures on full set of features using 16 cores & ssesdf \\
  \hline
\end{tabular}
\end{table}

@@

\glnote{To proofread / improve}

>>>>

As part of this work, we developed a stand-alone application for author
disambiguation, publicly available
online\footnote{\url{https://github.com/inveniosoftware/beard}} for free reuse
or study.  Our implementation builds upon the Python scientific stack, making
use of the Scikit-Learn library \citep{scikitlearn} for the supervised learning
of the similarity function and of SciPy \citep{scipy} for clustering. All
components of the disambiguation pipeline have been designed to follow the
Scikit-Learn API \citep{scikitlearnAPI}, making them easy to maintain,
understand and reuse.

\glnote{Not sure we should talk about parallelization?}
\glnote{Mention (future) deployment in Inspire?}

% Performance-wise, the clustering step appeared to be the bottleneck. We improved the
% algorithmic efficiency by parallelizing it. Having $n$ cores available, one can run the
% semi-supervised clustering for $n$ different blocks in the same moment. In the production
% systems the disambiguation often need not be run on the whole dataset. Once the dataset has
% been disambiguated once, it is possible to avoid rerunning the whole algorithm when the new
% signatures arrive in the digital library. First of all, the similarity function can be
% reused. Moreover, the clustering has to be applied only to the blocks the new signatures are
% contained within.

@@

\glnote{To review}
